Unsupervised embedding of trajectories captures the latent structure of mobility

### 2020-10-21 paper/current/main.tex
add more affiliation

\begin{document} %{{{
\title{Unsupervised embedding of trajectories captures the latent structure of mobility} %{{{
\author[1,\Yinyang]{Dakota Murray}
\author[1,2,\Yinyang]{Jisung Yoon}
\author[1]{Sadamori Kojaku}
\author[3]{Rodrigo Costas}
\author[2]{Woo-Sung Jung}
\author[1]{Staša Milojević \thanks{smilojev@indiana.edu}}
\author[1,4,5]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}

\affil[1]{Center for Complex Networks and Systems Research, Luddy School of Informatics, Computing, and Engineering, Indiana University, Bloomington, IN 47408, USA}
\affil[2]{Department of Industrial and Management Engineering, Pohang University of Science and Technology,
Pohang 37673, Republic of Korea.}
\affil[3]{Centre for Science and Technology Studies (CWTS), Leiden University, P.O. Box 905,
2300 AX Leiden, The Netherlands}
\affil[4]{Network Science Institute, Indiana University, Bloomington (IUNI), IN 47408, USA}
\affil[5]{Connection Science, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}

>>>>

\begin{document} %{{{
\title{Unsupervised embedding of trajectories captures the latent structure of mobility} %{{{
\author[1,\Yinyang]{Dakota Murray}
\author[1,2,\Yinyang]{Jisung Yoon}
\author[1]{Sadamori Kojaku}
\author[3]{Rodrigo Costas}
\author[2,4,5]{Woo-Sung Jung}
\author[1]{Staša Milojević \thanks{smilojev@indiana.edu}}
\author[1,6,7]{Yong-Yeol Ahn \thanks{yyahn@iu.edu}}

\affil[1]{Center for Complex Networks and Systems Research, Luddy School of Informatics, Computing, and Engineering, Indiana University, Bloomington, IN 47408, USA}
\affil[2]{Department of Industrial and Management Engineering, Pohang University of Science and Technology,
Pohang 37673, Republic of Korea.}
\affil[3]{Centre for Science and Technology Studies (CWTS), Leiden University, P.O. Box 905,
2300 AX Leiden, The Netherlands}
\affil[4]{Department of Physics, Pohang University of Science and Technology,
Pohang 37673, Republic of Korea.}
\affil[5]{Asia Pacific Center for Theoretical Physics, Pohang 37673, Republic of Korea.}

\affil[6]{Network Science Institute, Indiana University, Bloomington (IUNI), IN 47408, USA}
\affil[7]{Connection Science, Massachusetts Institute of Technology, Cambridge, MA 02139, USA}
